%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage{hyperref}
\setlist[itemize]{noitemsep, topsep=0pt}
\name{Siddhartha Thota} % Your name
% \address{56 Yarmouth Road, Toronto} % Your address
\address{Machine Learning Engineer}
\address{\href{http://www.cs.toronto.edu/~thota}{www.cs.toronto.edu/$\mathtt{\sim}$thota} \\ (416) 666 7834 \\ \href{mailto:sddhrthrt@gmail.com}{sddhrthrt@gmail.com} } % Your phone number and email

\begin{document}

\begin{rSection}{Objective}
Adaptable, passionate professional with over 3 years of proven experience deploying data science solutions to production. Aiming to learn fast while building elegant, maintainable products at my next job as a machine learning engineer.
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{StackAdapt}{\em Apr 2019 - Dec 2019}{Data Engineer}{Toronto, ON}
\vspace{-1mm}
\begin{itemize}
    \item Built demographic distribution reporting for ad campaigns using bayesian inference.
    \item Analyzed and eliminated mathematical inconsistencies in probabilistic data of user profiles in a distributed, billion-scale data warehouse using Spark in Scala.
    \item Developed data pipeline in Golang to write real-time, distributed data into Aerospike, then into a data lake, processed and analysed using Spark.
\end{itemize}

\end{rSubsection}

\begin{rSubsection}{ROSS Intelligence Inc.}{\em May 2018 - Dec 2018}{Machine Intelligence Engineer Intern}{Toronto, ON}
\vspace{-1mm}
\begin{itemize}
    \item Built novel query and case passage entailment detection with deep learning (attention-based LSTM).
    \item Explored a case annotation method using citation contexts with deep learning (PyTorch).
    \item Set up deep learning pipelines, deployed models-as-a-Service on AWS using Docker, EC2, Airflow.
    \item Built fast, reliable cached snippet highlighting for 14m casetexts (React, Scala, MongoDB on AWS).
    \item Improved user workflow and increased user retention with well-recognized hackday projects, using Chrome Extensions and React.
\end{itemize}

\end{rSubsection}

\begin{rSubsection}{Adobe Systems Inc.}{\em Jan 2016 - Aug 2017}{Member of Technical Staff - II}{Bangalore, India}
\vspace{-1mm}
\begin{itemize}
    \item Built v0.1 of the business unit's ML-as-a-service architecture for data preparation, model deployment and scoring (Azure, Docker with support for Python and Scala models).
    \item Developed a ML platform with Airflow on Mesos to deploy deep learning and SparkML models.
    \item Built UI to set up training, validation and deployment lifecycle of these models and provided visualization of their performance.
    \item Built framework to manage deployment of trained models and automatically generated inference APIs for use by dev teams.
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Adobe Systems Inc.}{\em June 2014 - Dec 2015}{Member of Technical Staff - I}{Bangalore, India}
\vspace{-1mm}
\begin{itemize}
    \item Built a platform for digital marketing clients to optimize spends on multiple channels, supporting multiple, parallel campaigns, 
    environment variables and revenue prediction.
    \item Overhauled the Marketing Mix Model and improved the optimizer performance 250x by optimizing data reads and storage ops.
    \item Cut UI response times 10x in report generation and caching using NumPy and Elasticache.
    \item Built ETL pipelines importing GBs of raw client data into data warehouse with schma-on-write.
\end{itemize}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\newpage
\begin{rSection}{Education}

{\bf University of Toronto, Canada} \hfill {\em Sept 2017 - Dec 2018} \\ 
MSc. in Applied Computing, GPA 3.925/4 \\
Research projects:
\vspace{-2mm}
  \begin{itemize}
    \item Pose-guided CycleGAN for Image to Image translation
    \item 8-month Machine Learning Engineer intern at ROSS Intelligence
    \item Sidewalk terrain estimation by clustering sensor data to assist wheelchair users
    \item Scheduling algorithms for applications on heterogenous multi-tier clouds
  \end{itemize}


{\bf National Institute of Technology Karnataka, India} \hfill {\em July 2010 - March 2014} \\ 
BTech. in Information Technology, GPA 8.47/10 \\
Research projects:
\vspace{-2mm}
  \begin{itemize}
    \item  Identifying ragas (musical modes in Indian classical music) using HMMs
  \end{itemize}


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Golang, Python, Scala, JS (React, etc) \\
ML \& Data Science & PyTorch, scikit-learn, Spark-MLLib, Pandas, TensorFlow \\
Frameworks & Spark, Docker, AWS/Azure, MongoDB, Aerospike etc. \\
Tools & Vim, git, linux, shell \\
\end{tabular}

\end{rSection}

% \begin{rSection}{Awards and Publications}
%   \begin{itemize}
%     \item Best poster award, CMU Winter School, Bangalore, 2012: Raga detection in Indian Classical Music using HMMs
%     \item Conference paper: Scale independent raga identification using chromagram patterns and swara based features (IEEE Explore) - IEEE, ICMEW, 2013
%   \end{itemize}
% \end{rSection}

\end{document}
